|

### 2019-07-03 R/README.Rmd
Update other README.md

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

@@

This directory contains R script files used throughout the project.

Each file contains several custom functions which have been
documented using roxygen2 skeletons.

# contents
```
    .
    ├── ...
    ├── /R
    │    ├── file1.R          # Functions for x
    │    ├── file2.R          # Functions for y
    │    ├── file3.R          # Functions for z
    │    ├── README.Rmd       # R markdown file to produce README.md
    │    └── README.md        # Description of /R directory
    └── ...

```

>>>>

```{r, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>")
```

@@

## Description

This directory contains R script files used throughout the project. Each file 
contains one custom function or one data.frame which has been
documented using an roxygen2 skeleton.

After installing `candidaev`, an index of all the included 
functions/data.frames can be viewed in R using:

```{r, eval=FALSE}
help(package = "candidaev")
```

### 2019-07-03 data-raw/README.Rmd
Update other README.md

## description
This directory contains all of the raw data files used in this project. These files are
*not* included when the package is installed using `devtools::install_github()`. Rather 
*'clean'* versions of the `.csv` and `.tab` files are provided in the [`/data`](../data) 
folder as `.rda` files which are accessible once the package has been installed and 
loaded or attached.

To access these raw files:

@@

4. Clone this repository.

## contents
```
    .
    ├── ...
    ├── /data-raw
    │    ├── /external       # Supplementary data tables from other Candida EV proteomics papers
    │    ├── /lcms           # proteinGroups.txt files output by MaxQuant
    │    ├── /nta            # Nanosight ns300 .csv summary tables
    │    ├── /qubit          # Qubit 4 EV protein quantification data 
    │    ├── /reference      # UniProt and Candida Genome Database reference tables
    │    ├── README.Rmd      # R markdown file to produce README.md
    │    └── README.md       # Description of /data-raw directory
    └── ...

>>>>

## Description
This directory contains all of the raw data files used in this project. 
These files are *not* included when the package is installed using 
`devtools::install_github()`. Rather *'clean'* versions of the `.csv` and 
`.tab` files are provided in the [`/data`](../data) folder as `.rda` files 
which are accessible once the package has been installed and loaded or attached.

Some different ways to access these raw files include:

@@

4. Clone this repository using `git`.

## Contents
```
    .
    ├── ...
    ├── /data-raw
    │    ├── /lcms           # proteinGroups.txt files output by MaxQuant
    │    ├── /nta            # Nanosight NS300 .csv summary tables
    │    ├── /reference      # UniProt and Candida Genome Database reference tables
    │    ├── README.Rmd      # R markdown file to produce README.md
    │    └── README.md       # Description of /data-raw directory
    └── ...

### 2019-07-03 inst/manuscript/README.Rmd
Update other README.md

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# /vignettes

## description
This directory contains the submitted manuscript (see `manuscript.pdf`) 
for this paper :

> Authors, (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>

It also contains a more detailed analysis of the LC-MS/MS data, upon which the manuscript 
is based (see `analysis.md` or `analysis.html`). The 
Rmarkdown (`.Rmd`) files used to generate these documents are provided.

Both the manuscript and the analysis documents *are* included as vignettes in this 
package so they can be easily viewed (or regenerated completely from the raw data) if 
the package is installed. Alternatively, one can download these documents directly 
from this GitHub repository.

## how to access the manuscript

## how to access the analysis

## contents
```
    .
    ├── ...
    ├── /vignettes
    │    ├── /figures            # Contains figures
    │    ├── /components         # Contains required components for knitting manuscript and analysis
    │    ├── analysis.Rmd        # R markdown file to produce analysis.md or analysis.html
    │    ├── analysis.html       # Full analysis upon which the manuscript is based.
    │    ├── analysis.md         # Full analysis upon which the manuscript is based.
    │    ├── manuscript.Rmd      # R markdown file to produce manuscript.pdf or manuscript.docx
    │    ├── manuscript.pdf      # Final submitted manuscript
    │    ├── README.Rmd          # R markdown file to produce README.md
    │    └── README.md           # Description of /vignettes directory
    └── ...

>>>>

```{r, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>")
```

# /inst/manuscript

## Description

This directory contains the submitted manuscript, supplemental figures and 
tables, and supplemental files for our paper:

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins and Rho GTPases. Mol. Cell. Proteomics, 
submitted.

The Rmarkdown (`.Rmd`), `.svg`, and `.R` files used to generate these 
documents are provided along with the derived `.pdf` and `.csv` files.

## Contents
```
    .
    ├── ...
    ├── /inst
    │    ├── /manuscript
    │         ├── /components                 # Contains required components for building the manuscript
    │         ├── /figures                    # Contains .svg and .csv files used to make some figures
    │         ├── /supplement_files           # Contains .R scripts used to generate supplemental files
    │         ├── manuscript.Rmd              # R markdown file to produce manuscript.pdf
    │         ├── manuscript.pdf              # Final submitted manuscript
    │         ├── manuscript_supplement.Rmd   # R markdown file to produce manuscript_supplement.pdf
    │         ├── manuscript_supplement.pdf   # Final submitted supplemental figures and tables
    │         ├── README.Rmd                  # R markdown file to produce README.md
    │         └── README.md                   # Description of /inst/manuscript directory
    └── ...
